---
title: "fars_details"
author: "Vinh Hang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fars_details}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Intro

The package includes 5 functions: 
<ol>
<li>fars_read to read in data from a given years</li>
<li>make_filename </li>
<li>fars_read_years to return a list of month and years of the fars data</li>
<li>fars_summarize_years to summarize total accidents by months and years</li>
<li>fars_map_state plots the fars data on a given state and year</li>
</ol>

## Dependencies

While it may not be neccesary, the following package will ensure the above functions run smoothly: dplyr, tidyr, readr and maps

```{r loading packages}
library(dplyr)
library(readr)
library(tidyr)
library(maps)
library(fars)
```

## How it works?

Lets read in the fars for 2013 data. Of course you can also use make_filename to create the file name. All the exploratory work should starts here before proceeding to the next functions.

```{r read data}
file <- make_filename(2013)
data <- fars_read(filename = file)
dim(data)
head(names(data))
```


## fars_read_year

If Month and years of the accidents are the only things you want, then fars_read_year can be called. Moreover, the fars_summarize_years will take that result and output a summary of total accidents by months/year 

```{r fars read year}
data <- fars_read_years(c(2013, 2014))
data <- fars_summarize_years(c(2013, 2014))
data
```

## fars_map_state

Lastly, the fars_map_state function will plot the total accidents by state and year. 

```{r plot on map}
fars_map_state(state.num = 31, year = 2013)
```
